The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/accuracy.tex
Rewrote accuracy section (again)

We are naturally most interested in cases where other solutions perform poorly.
Recall that when $n$ is small, it is feasible to calculate the binomial
directly, and when $n$ is large or $p$ is close to 0.5, the normal distribution
provides an adequate approximation. Therefore, our interest is primarily in
cases where $n$ is moderate and $p$ is extreme (close to 0 or 1).\footnotemark

@@

Figure \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
\ref{app:figures} shows the MABS of the skew-normal and normal approximations
as a function of $p$ and $n$, respectively.

In figure \ref{fig:mabs-fixed-n}, the MABS of the normal approximation is more
than four times that of the skew-normal when $p$ is very close to 0. The two
error curves converge and eventually meet as $p$ approaches 0.5 and the
binomial becomes symmetrical.

Similarly, in figure \ref{fig:mabs-fixed-p}, the normal MABS is roughly six
times the skew-normal MABS. Interesting, the error curves converge much more
slowly this time, leading to the pleasant (if surprising) conclusion that when
$p$ is extreme, the skew-normal gains us a measure of accuracy even at very
large $n$.

>>>>

We are naturally most interested in cases where other solutions perform poorly.
Recall that when $n$ is small, it is feasible to execute the binomial
calculations directly, and when $n$ is large or $p$ is close to 0.5, the normal
distribution provides an adequate approximation. Therefore, our interest is
primarily in cases where $n$ is moderate and $p$ is extreme (close to 0 or
1).\footnotemark

@@

Figure \ref{fig:mabs-fixed-n} in appendix \ref{app:figures} shows the MABS of
the skew-normal and the normal approximations as a function of $p$ for $n=25$
and $n=100$. When $p$ is very close to 0, the MABS of the normal approximation
is more than four times that of the skew-normal, again demonstrating the
benefit of using the skew-normal approximation for moderate $n$ and extreme
$p$. The two error curves converge and eventually meet as $p$ approaches 0.5.

Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS of our two
approximations as a function of $n$ for $p=0.05$ and $p=0.1$. At small to
moderate $n$, the normal MABS is roughly six times the skew-normal MABS.
Interestingly, the error curves converge much more slowly this time, leading to
the pleasant (if surprising) conclusion that when $p$ is extreme, the
skew-normal gains us a measure of accuracy even at large $n$.
